
\cvsection{Achievements}
\begin{itemize}
\item Government Bug Bounty Appreciation - NCIIPC appreciated my endeavour towards securing the Nation's cyberspace.
\item Appreciation from IIT-G for finding a vulnerability in their Website.
\item Received Reputation on Hackerone's Private Program.
\item Ranked 40(in India) on the Tryhackme platform.
\end{itemize}

\cvsection{Projects}
\cvproject{Security Guide}
\begin{itemize}
\item A React JS and JAMstack based website which guides people about cybersecurity. 
\end{itemize}

\cvproject{Port Scanner}
\begin{itemize}
\item A python based tool which help the user find out all the open ports in a system.
\end{itemize}

\cvproject{Twillio based video App}
\begin{itemize}
\item A Node JS web application created to video call friends.This was created using the Twillio's video calling  API and Gatsby.  
\end{itemize}

\cvproject{Safe Plugin}
\begin{itemize}
\item A prototype of an Application which provides the functionality to prevent HID based attacks on a system.
\end{itemize}

\cvproject{Smart Farming }
\begin{itemize}
\item Automation Product which is used to automate the farming needs.
\end{itemize}

\cvproject{Badauino }
\begin{itemize}
\item An Arduino based malicious USB.  
\end{itemize}

\cvproject{Covid19cases}
\begin{itemize}
\item An Automation program written in python to scrape data from the MoHFW's websites and present in the chart format on a React JS based website
\end{itemize}
\cvsection{SKILLS}
\cvskill{Nmap, Metasploit, Wireshark}{5}
\cvskill{BurpSuite.Vega, Maltego}{5}
\cvskill{Python, Bash, Linix}{4}
\cvskill{Rasberry pi, IOT,AWS,GCP}{3}
\cvskill{OWASP TOP 10,Latex}{4}
\cvskill{JavaScript, Html, Nodejs}{3}
\cvskill{Acunetix,Nesses,Nexpose} {3}

\cvsection{Conferences}
\begin{itemize}
\item Attendee at Summer school of security in computing workshop, JIIT NOIDA. 
\item Attendee at Google cloud platform fundamentals workshop, Google Onboard Delhi.
\item Attendee at BSides Delhi, a security conference organised by the BSides community
\item \end{itemsize}
\end{itemize}

